%-------------------------
% Resume in Latex
%------------------------

\documentclass[a4paper,11pt]{article}

\usepackage{latexsym}
\usepackage{xcolor}
\usepackage{float}
\usepackage{ragged2e}
\usepackage[empty]{fullpage}
\usepackage{wrapfig}
\usepackage{tabularx}
\usepackage{titlesec}
\usepackage{geometry}
\usepackage{marvosym}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{graphicx}
\usepackage[T1]{fontenc}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% FIXED: tighter margins to use more of the page
\geometry{left=1.4cm, top=0.6cm, right=1.2cm, bottom=0.8cm}

\urlstyle{same}
\raggedright
\setlength{\tabcolsep}{0in}

% FIXED: reduced vspace before section title
\titleformat{\section}{
  \vspace{-6pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands

\newcommand{\resumeSubheading}[4]{
\vspace{0.5mm}\item
\begin{tabular*}{0.98\textwidth}[t]{l@{\extracolsep{\fill}}r}
\textbf{\small #1} & \textit{\small #4} \\
\textit{\small #3} & \small #2\\
\end{tabular*}
\vspace{-2mm}
}

\newcommand{\resumeProject}[3]{
\vspace{0.5mm}\item
\begin{tabular*}{0.98\textwidth}[t]{l@{\extracolsep{\fill}}r}
\textbf{\small #1} & \textit{\small #3} \\
\small\textit{#2}
\end{tabular*}
\vspace{-2mm}
}

\renewcommand{\labelitemi}{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*,labelsep=0mm,topsep=0pt]}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=3ex, rightmargin=2ex, topsep=0pt, itemsep=-1pt]\small}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-2mm}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%

\newcommand{\name}{Ankit Singh Kushwah}
\newcommand{\course}{B.Tech (Hons.) Computer Science}
\newcommand{\phone}{8839808758}
\newcommand{\emaila}{ankitask46@gmail.com}

\begin{document}

\fontfamily{cmr}\selectfont

%----------HEADING-----------------

\begin{tabularx}{\linewidth}{l X r}
\textbf{\Large \name} & & {\small \faPhone\ +91-\phone} \\[2pt]
\small RV University & & \href{mailto:\emaila}{\small \faEnvelope\ \emaila} \\[2pt]
\small\course & & \href{https://github.com/ankit4563564}{\small \faGithub\ GitHub Profile} \\[2pt]
\small Expected Graduation: 2028 & & \\
\end{tabularx}

\vspace{2mm}

%-----------EDUCATION-----------

\section{\textbf{Education}}

\resumeSubHeadingListStart

\resumeSubheading
{RV University}{CGPA: 8.1}
{B.Tech (Hons.) Computer Science}{2024 -- 2028}

\resumeSubheading
{Kendriya Vidyalaya, Raipur}{Percentage: 75\%}
{CBSE Class XII}{2024}

\resumeSubheading
{Kendriya Vidyalaya, Raipur}{Percentage: 91.8\%}
{CBSE Class X}{2022}

\resumeSubHeadingListEnd

\vspace{-1mm}

%-----------PROJECTS-----------------

\section{\textbf{Personal Projects}}

\resumeSubHeadingListStart

\resumeProject
{Glamora --- AI-Powered Grooming Marketplace\ \normalfont\small| \href{https://github.com/ankit4563564/GLAMORA-1}{\small\textcolor{blue}{\faGithub}}}
{Bangalore's premium grooming marketplace with AI-driven discovery, facial analysis, and conversational booking.}
{2025}

\resumeItemListStart
\item Built AI Agent using Gemini 2.0 Flash for natural salon search and booking conversations, reducing booking time by 60\%.
\item Implemented BeautyAI with Gemini 1.5 Flash Vision for facial analysis, processing image uploads in under 3 seconds with Cloudinary optimization.
\item Designed MongoDB schema for 4,500+ salons with compound indexes for efficient location-based search and booking conflict prevention.
\item Developed enterprise owner dashboard with Recharts analytics and AI-generated marketing copy using Groq SDK.
\item \textbf{Tech:} Next.js 14, TypeScript, MongoDB Atlas, Clerk Auth, Tailwind CSS, Framer Motion, Recharts, Cloudinary, Mongoose, Radix UI, Leaflet, Zod
\resumeItemListEnd

\resumeProject
{PGions --- Full-Stack Coliving Platform\ \normalfont\small| \href{https://pgions.vercel.app/}{\small\textcolor{blue}{\faGlobe}} \href{https://github.com/ankit4563564/Pgions}{\small\textcolor{blue}{\faGithub}}}
{PG discovery platform with trust verification, roommate matching, and rental agreement generation.}
{2025}

\resumeItemListStart
\item Developed Vibe-Match compatibility engine with quiz-based scoring on budget, sleep schedule, cleanliness, and dietary preferences.
\item Built Z-Scam Shield verification system with severity-based flagging (high/medium risk) to detect and warn about suspicious listings.
\item Implemented Trust Score algorithm evaluating properties across 20+ parameters including owner verification, reviews, and response times.
\item Created PDF rental agreement generator using jsPDF with multi-step form for tenant/owner details and legal terms.
\item Built Fair Rent Split Calculator with perk-based distribution (window bed, attached washroom, AC) for shared accommodations.
\item Developed in-app visit scheduling system with time slot selection and status tracking via Prisma ORM.
\item Implemented secure chat system for roommate communication and property inquiries.
\item Deployed on Vercel with PostgreSQL database and NextAuth.js authentication (Google OAuth + credentials).
\item \textbf{Tech:} Next.js 16, React 19, Prisma ORM, PostgreSQL, NextAuth.js, jsPDF, CSS Modules, Lucide React
\resumeItemListEnd

\resumeSubHeadingListEnd

\vspace{-1mm}

%-----------TECHNICAL SKILLS-----------------

\section{\textbf{Technical Skills}}

\begin{itemize}[leftmargin=0.05in, label={}, topsep=2pt, itemsep=1pt]
\item\small{

\textbf{Languages: } C++, JavaScript, Python, Java, TypeScript \\[1pt]
\textbf{Frontend: } React.js, Next.js, HTML, CSS, Tailwind CSS, Framer Motion \\[1pt]
\textbf{Backend: } Node.js, Express.js, PHP \\[1pt]
\textbf{Databases: } MongoDB, MySQL, PostgreSQL, Prisma ORM \\[1pt]
\textbf{Developer Tools: } Git, GitHub, VS Code, Postman \\[1pt]
\textbf{Coursework: } Data Structures, OOPs, DBMS, Operating Systems \\[1pt]
\textbf{Soft Skills: } Leadership, Teamwork, Communication, Problem Solving \\

}
\end{itemize}

\vspace{-1mm}

%-----------ACHIEVEMENTS / EXTRA (placeholder to fill page)-----------------
% Uncomment and fill if you have achievements, certifications, or positions of responsibility

%\section{\textbf{Achievements \& Certifications}}
%\resumeSubHeadingListStart
%\resumeProject{Certification Name}{Issued by Organization}{2025}
%\resumeItemListStart
%\item Brief description of what was achieved or learned.
%\resumeItemListEnd
%\resumeSubHeadingListEnd

%-------------------------------------------

\end{document}
